---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Future

<!-- badges: start -->
[![R-CMD-check](https://github.com/FUTUR-TEAM/Future/workflows/R-CMD-check/badge.svg)](https://github.com/FUTUR-TEAM/Future/actions)
[![Coveralls test coverage](https://coveralls.io/repos/github/FUTUR-TEAM/Future/badge.svg)](https://coveralls.io/r/FUTUR-TEAM/Future?branch=main)
<!-- badges: end -->

Future is a tool for creating healthy meals. You can calculate your BMI, calculate energy value of preparing meal and calculate glycemic index of this meal.

## Installation

You can install the development version of Future from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FUTUR-TEAM/Future")
```
## Example

By default, Future was prepared as Shiny app, but you can use single function from command line.
This is a basic example which shows you how to calculate percent of macronutrients of meal from lists of using products and their weights

```{r example}
library(Future)

df <- data.frame(products = c("Banan","Kawior"), weight = c(50,50), stringsAsFactors = FALSE) 

macro_df <- macronutrients_of_meal(as.list(df$products), as.list(df$weight))
macro_df
macro_percent_graph(macro_df)
```
